Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-17 manuscript/manuscript.Rmd
3d model section done (up to figures)

Most commonly, fisheries use 1-dimensional models, $n=1$.
One such model appearing in a variety of ecological contexts is *logistic growth*, for which
$$
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
$$
More relevant to our current work, is the following single-species model studied in \cite{may77},
\begin{align}
  \label{eq:may}
  X_{t+1} - X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c),
\end{align}
where,
\begin{align*}
  F(X,H;\ \beta,c) := \frac{\beta H X^2}{c^2 + X^2}.
\end{align*}
The model has five parameters: the growth rate $r$ and carrying capacity $K$ for $X$, a constant population $H$ of a species which preys on $X$, the maximal rate of predation $\beta$, and the predation half-maximum biomass $c$.

@@

>>>>

Most commonly, fisheries use 1-dimensional models, $n=1$.
One such model appearing in a variety of ecological contexts is *logistic growth*, for which
$$
  f(X_t) = r X_t\big(1 - X_t / K \big) =: L(X_t;\ r, K).
$$
More relevant to our current work, is the following single-species model studied in \cite{may77},
\begin{align}
  \label{eq:may}
  X_{t+1} - X_t
  = L(X_t;\ r, K) - F(X_t, H; \beta,c) - h_t,
\end{align}
where,
\begin{align*}
  F(X,H;\ \beta,c) := \frac{\beta H X^2}{c^2 + X^2}.
\end{align*}
The model has five parameters: the growth rate $r$ and carrying capacity $K$ for $X$, a constant population $H$ of a species which preys on $X$, the maximal rate of predation $\beta$, and the predation half-maximum biomass $c$.

@@

As can be expected, the dynamics of eq. \eqref{eq:3d model} are significantly more complex than those of eq. \eqref{eq:may}.
There are a variety of fixed points for the equations---around 7 or 8 for wide ranges of parameter values.
Fig. \ref{fig:tbd} provides a rough idea of the fixed point structure by plotting the bifurcation diagram obtained from varying $D$ and fixing the other parameters.

Throughout most of this paper we will fix the parameters of the model according to Table \ref{tab:tbd}.
At these values, the fixed points of the model are:
\begin{align*}
  TBD
\end{align*}
The classification of fixed points for multi-dimensional systems is generally more complicated than in one dimension.
A fixed point might be stable against perturbations in one direction, but unstable against perturbations along another.
While a detailed classification of these fixed points is beyond the scope of this work, we point out that the point $(TBD)$ is stable against perturbations in all directions.
We will thus use it as a starting point for our simulations.
